% ===============================================================================================
% ===============================================================================================
% =====================================Conference Logistics======================================
% ===============================================================================================
% ===============================================================================================

\section{Conference Logistics}

\subsection{Date Selection}
Primary date selection\\
Rationale for date selection\\
Graphical calendar of date selection and conflicts\\

We are aware that there is no perfect date in which everyone who wants to attend the conference can do so. However, our hope is to accommodate as many students as possible with a proposed date of either: Thursday April 8th - Saturday April 10th or Thursday April 15th - April 17th, 2021. Two dates are proposed because the Mom's association that runs Mom's Weekend, one of the largest events of the year, has not announced their 2021 dates yet. Mom's weekend is typically held the first weekend of April which conflicts with Easter in 2021. This consensus was reached after looking up any holidays, scheduled spring breaks, final exams, and other miscellaneous conflict dates for 42 schools with active ANS student sections. Based on these findings, there are no major conflicts with any of the schools for these dates. These factors were considered in order to maximize the possible number of attendees that can benefit from the conference. A handful of schools did not have an academic calendar available for the 2021 Spring semester, so data was based on their listed 2020 dates. These date selections avoid conflicting with large event weekends such as Mom's Weekend, dates pending, and the Illini Marathon. If, for some reason, an issue arises with our proposed dates, our back-up date is Thursday April 1st - Saturday April 3rd. This is unfortunately the same weekend as Easter Sunday. However, we prioritized avoid final exams, and UIUC’s Mom’s Weekend. Please see the appendix for the full conflicts calendar.

\subsection{Conference Facilities}
\begin{itemize}
  \item \textbf{The Illini Union}\\
  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
  \item \textbf{Beckman Institute}\\
  \item \textbf{The I-Hotel}\\
  \item \textbf{}\\
\end{itemize}



\subsection{Conference Contingency Plan}
\subsection{Hotels and Accomodations}

$\Large\textbf{Illini Union}$\\

$\Large\textbf{Marriott TowneSuites}$\\

$\Large\textbf{Hyatt}$\\

\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Below are the round-trip, non-stop, airfare costs for the first weekend of April.  
\begin{center}
	\begin{tabular}{lcc}
		\hline\hline
		\textbf{School} & \textbf{Departure City} & \textbf{Airfare to O'Hare (ORD)*}\\
		\hline\hline
		University of Florida & Orlando (ORL) & $\$$ 236\\
		Texas A$\&$M & College Station (CLL)& $\$$ 393\\
		Penn State University & State College (SCE) & $\$$ 349\\
		MIT & Boston (BOS) & $\$$ 217\\
		UNLV & Las Vegas (LAS) & $\$$ 308\\
		Georgia Tech & Atlanta (ATL) & $\$$ 175\\
		University of Michigan & Detroit (DTW) & $\$$ 240\\
		Oregon State University & Portland (PDX) & $\$$ 355\\
		RPI & Albany (ALB) & $\$$ 504\\
		UC Berkley & Oakland (OAK) & $\$$ 674\\
		UC Irvine & Orange County (SNA) & $\$$ 439\\
		US Naval Academy & Baltimore (BWI)& $\$$ 383\\
		University of Marlyand & Baltimore (BWI) & $\$$ 383\\
		University of Missouri-Columbia & St. Louis (STL) & $\$$ 168\\
		University of Nevada & Reno (RNO) & $\$$ 374\\
		University of New Mexico & Albuqurque (ABQ) & $\$$ 477\\
		NC State  University & Raleigh (RDU) & $\$$ 195\\
		University of Pittsburgh& Pittsburgh (PIT) & $\$$ 271\\
		Clemson University & Greenville (GSP) & $\$$ 295\\
		SC State University & Columbia (CAE) & $\$$ 365\\
		University of South Carolina & Columbia (CAE) & $\$$ 365\\
		Brigham Young University & Salt Lake City (SLC) & $\$$ 441\\
		U. Wisconsin-Madison & Madison (MSN) & $\$$ 229\\
		Colorado School of Mines & Denver (DEN)& $\$$ 223\\
		University of  Tennessee-Knoxville & Knoxville (TYS) & $\$$ 279\\
		Virginia Commonwealth University & Richmond (RIC) & $\$$ 326 \\
		Iowa State University & Des Moines (DSM) & $\$$ 199 \\
		University of Iowa & Cedar Rapids (CID) & $\$$ 249 \\
	\end{tabular}	
\end{center}
\textbf{*}\textit{These fares are predicted to go down around February and March.}\\

Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities. 
\begin{center}
	\begin{tabular}{l r}
	\hline\hline
	\textbf{School}& \textbf{Drive Time}\\
	\hline\hline
	U. Tennessee Knoxville & 7 h 13 min\\
	University of Michigan & 5 h 24 min\\
	Clemson University & 10 h 5 min\\
	U. Missouri-Columbia & 4 h 18 min\\
	Georgia Tech University & 8 h 54 min \\
	University of Pittsburgh & 7 h 19 min\\
	U. Wisconsin-Madison & 3 h 53 min \\
	Penn State University & 9 h 17 min\\
	University of South Carolina& 10 h 44 min\\
	Iowa State University & 5 h 24 min \\
	University of Iowa & 3 h 34 min\\
	Vanderbilt University & 5 h 18 min\\
	\end{tabular}
\end{center}
