\section{Website and Social Media}
\subsection{Website}
Shortly after the host is announced, ANS-UIUC will purchase a domain name and create a website in conjunction with ANS National. The website will be hosted using GitHub pages, a free hosting service for static websites. Since there is no cost, the website can be hosted indefinitely. This webhost was selected because several members of the chapter possess knowledge and experience in using it for serving collaborative, Jekyll-based, and static websites. The domain name can be purchased for as little as one dollar for the first year, and a little less than $\$20$ to maintain annually. If we need to cut costs or decide that a domain name ending in ".github.io" is fine we can drop the purchased domain name. The website will include important dates, costs, calendars, schedules, maps, emergency contact information, as well as a direct link to the paper submission site for the conference. The mobile web app will store downloaded maps, emergency contact information, and calendars for offline use while providing access to all features of the website as well.

\subsection{Social Media} 
Two accounts will be used to monitor and promote social media at the event. The first will be a Twitter account, created specifically for the conference. This account will send out schedules and updates, as well as neat facts about events at the conference. The second account will be a Facebook page which will serve a similar function to the Twitter account. The Facebook page has the added benefit of being able to create events. This ability would be used to provide another source of schedule information to conference attendees. 